A new breeding crossover approach for evolutionary algorithms

### 2023-09-20 paper.tex
Figure Enlargement

    One essential feature to highlight in the algorithm is that it doesn't use the concept of generations in the evolution. Our strategy views the population as a set of candidate solutions that evolve continuously over time, which allows individuals of multiple ages to reproduce and generate new offspring, reflecting nature's actual behavior. Another difference to highlight in our algorithm is that both reproduction (crossover) and growth (mutation) execute through independent processes that randomly affect the population. Figure~\ref{fig.algorithm_model} displays the general model concept for the Animal Life Cycle Algorithm (ALCA).

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.90\linewidth]{img/fig_algorithm_model.pdf}
        \caption{Animal Life Cycle Algorithm model.} \label{fig.algorithm_model}
        \end{figure}

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.70\linewidth]{img/fig_grayscale_continuous.pdf}
        \caption{Black and white offspring, predictable color domain.} \label{fig.grayscale_continuous}
        \end{figure}

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.50\linewidth]{img/fig_onepoint_crossover.pdf}
        \caption{Classical approach example for the One Point Crossover, with crossover point 3.} \label{fig.onepoint_crossover}
        \end{figure}

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.50\linewidth]{img/fig_contrange_crossover.pdf}
        \caption{Our proposal example for the Continuous Range Crossover mating the same couple of individuals.} \label{fig.contrange_crossover}
        \end{figure}

@@

\begin{acknowledgement}
    This paper has been supported in part by TecNM Project 18186.23-P.
\end{acknowledgement}

>>>>

    One essential feature to highlight in the algorithm is that it doesn't use the concept of generations in the evolution. Our strategy views the population as a set of candidate solutions that evolve continuously over time, which allows individuals of multiple ages to reproduce and generate new offspring, reflecting nature's actual behavior. Another difference to highlight in our algorithm is that both reproduction (crossover) and growth (mutation) execute through independent processes that randomly affect the population. Figure~\ref{fig.algorithm_model} displays the general model concept for the Animal Life Cycle Algorithm (ALCA)\cite{Felix-Saul2023}.

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.90\linewidth]{img/fig_algorithm_model.pdf}
        \caption{Animal Life Cycle Algorithm model\cite{Felix-Saul2023}.} \label{fig.algorithm_model}
        \end{figure}

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.90\linewidth]{img/fig_grayscale_continuous.pdf}
        \caption{Black and white offspring, predictable color domain.} \label{fig.grayscale_continuous}
        \end{figure}

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.90\linewidth]{img/fig_onepoint_crossover.pdf}
        \caption{Classical approach example for the One Point Crossover, with crossover point 3.} \label{fig.onepoint_crossover}
        \end{figure}

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.90\linewidth]{img/fig_contrange_crossover.pdf}
        \caption{Our proposal example for the Continuous Range Crossover mating the same couple of individuals.} \label{fig.contrange_crossover}
        \end{figure}

@@

\begin{acknowledgement}
    TecNM Project 18186.23-P has partially funded this research.
\end{acknowledgement}
